% Chapter: Methodology
\section{Methodology}

This work implements a structured, prototype-level pipeline for the early-stage design of drone light show formations. The methodology emphasizes the integration of generative visual inputs with deterministic analytical validation, reflecting the separation between semantic intent and syntactic execution that characterizes professional workflows. The pipeline proceeds from image acquisition to point sampling, Skybrush-based validation, and final compilation into deployable formats.

\subsection{Workflow Analysis}

The development of the pipeline begins with an examination of existing drone show design workflows. Although the project does not replicate full production practices, it draws on publicly available documentation and demonstrations from commercial platforms such as SPH Engineering's Drone Show Software, Verge Aero's Design Studio, and Skybrush Studio. These materials clarify the structure of professional pipelines, the constraints imposed during formation design, and the requirements for producing validated flight plans. This analysis ensures that the implemented system remains aligned with real operational expectations, even in a constrained prototype form.

\subsection{Pipeline Architecture}

The implemented pipeline is modular and reflects a progression from creative input toward analytical enforcement. It consists of four principal stages:

\begin{enumerate}
  \item \textbf{Image Acquisition:} The pipeline begins with a visual reference supplied either directly by the user or generated via lightweight prompting through an external model. This image represents the semantic intent of the designer and provides the basis for subsequent formation extraction.

  \item \textbf{Point Sampling:} The reference image is converted into a binary silhouette, from which a fixed number of drone positions are sampled. Several sampling strategies were evaluated, including grid sampling, blue-noise sampling, and farthest-point sampling. The latter proved most effective at preserving recognizable structure while maintaining minimum spacing between points.

  \item \textbf{Skybrush Integration:} Sampled coordinates are exported as \texttt{.csv} files and imported into Skybrush Studio via its Blender extension. Within this environment, the sampled formation can be visualized and inspected using the same interface employed in professional drone show design.

  \item \textbf{Validation and Export:} Skybrush Studio performs analytical checks on spacing and formation feasibility. Once validated, the formation can be compiled into deployable formats such as \texttt{.skyc}, enabling downstream integration with compatible drone control software.
\end{enumerate}

This architecture demonstrates how generative or user-driven visual concepts can be translated into syntactically valid formation data through established analytical tools.

\subsection{Integration with Skybrush Studio API}

Although the pipeline primarily uses the Blender-integrated interface of Skybrush Studio, its design aligns with the capabilities of the Skybrush Studio API, which exposes programmatic endpoints for safety verification and binary compilation. The system's reliance on industry-grade validation tools illustrates how generative front ends can be coupled with existing production infrastructures without modifying their internal logic. This highlights the feasibility of modular semantic-syntactic integration in a realistic workflow.

\subsection{Evaluation}

The evaluation focuses on qualitative and structural criteria rather than numerical performance metrics. Specifically, the pipeline is assessed on:

\begin{itemize}
  \item \textbf{Sampling Fidelity:} The extent to which each sampling method preserves the recognizable structure of the input silhouette.
  \item \textbf{Feasibility in Skybrush:} Whether the exported formations import cleanly and satisfy spacing constraints as enforced by Skybrush Studio.
  \item \textbf{Workflow Coherence:} The clarity of the transformation from image input to validated formation, emphasizing interpretability and modularity.
\end{itemize}

Evaluation is supported by visual inspection of sampled point sets and their rendered counterparts in Skybrush Studio.

\subsection{Limitations}

The methodology is constrained by its focus on static 2D formations. It does not generate or optimize temporal transitions, and it does not incorporate full 3D formation sampling or trajectory planning. The use of external image-generation tools captures only a narrow slice of semantic input, and the analytical validation depends on the capabilities provided by Skybrush Studio. While these constraints reflect the prototype nature of the system, they do not undermine its central aim: to demonstrate a coherent workflow linking conceptual imagery to analytically validated drone formations.

Despite these limitations, the methodology establishes a reproducible framework that illustrates how generative inputs and analytic solvers can be coupled in practice. This provides a foundation for future work in extending the pipeline to dynamic, 3D, or fully integrated generative-analytic systems.

